A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-09-04 rr-flow.Rmd
add liftr package closes #41

While this approach here was designed to scale well with the complexity of a computing-intense Project, we realise that this flexibility comes with a steep learning curve. A few packages are easing this burden for different parts of the workflow when this flexibility is not needed. The use of `rmarkdown` within a project, tracked with `git` can be simplified with the [workflowr-package](https://github.com/jdblischak/workflowr) [@workflowr]. The [drake-package](https://github.com/ropensci/drake) [@drake] is directly inspired by `make` but does only require knowledge in R, but can only handle dependencies within R. The [holepunch-package](https://karthik.github.io/holepunch/) [@holepunch] automizes the use of docker and uses [binder](https://mybinder.org) to move the analysis to the cloud so that no local installation of docker is required. It is well suited for simple analysis with low computational demands, because of memory and computing time limitations of binder. There are several alternatives to docker which fix the dependencies on R-packages. [packrat](https://rstudio.github.io/packrat/) [@packrat] is a way to fix package version via local installations of packages in the project, however it does not garuantees more then a fixed set of packages (Not R-version or system dependencies). Similar approaches are taken by [jetpack](https://github.com/ankane/jetpack) [@jetpack], [miniCRAN](https://cran.r-project.org/web/packages/miniCRAN/vignettes/miniCRAN-introduction.html) [@miniCRAN] and [checkpoint](https://cran.r-project.org/web/packages/checkpoint/vignettes/checkpoint.html) [@checkpoint]. Notable is also the package [`reprex`](https://github.com/tidyverse/reprex) [**repr**oducible **ex**ample, @reprex], but its scope is limited to small examples.

>>>>

While this approach here was designed to scale well with the complexity of a computing-intense Project, we realise that this flexibility comes with a steep learning curve. A few packages are easing this burden for different parts of the workflow when this flexibility is not needed. The use of `rmarkdown` within a project, tracked with `git` can be simplified with the [workflowr-package](https://github.com/jdblischak/workflowr) [@workflowr]. The [drake-package](https://github.com/ropensci/drake) [@drake] is directly inspired by `make` but does only require knowledge in R, but can only handle dependencies within R. The [liftr-package](https://cran.r-project.org/web/packages/liftr/vignettes/liftr-intro.html) [@liftr] and the [holepunch-package](https://karthik.github.io/holepunch/) [@holepunch] automize the use of docker. The former is perfectly compatible with the described workflow and we recommend it to user uncomftable with docker. The later uses [binder](https://mybinder.org) to move the analysis to the cloud so that no local installation of docker is required. holepunch is well suited for simple analysis with low computational demands, because of memory and computing time limitations of binder. There are several alternatives to docker which fix the dependencies on R-packages. [packrat](https://rstudio.github.io/packrat/) [@packrat] is a way to fix package version via local installations of packages in the project, however it does not garuantees more then a fixed set of packages (Not R-version or system dependencies). Similar approaches are taken by [jetpack](https://github.com/ankane/jetpack) [@jetpack], [miniCRAN](https://cran.r-project.org/web/packages/miniCRAN/vignettes/miniCRAN-introduction.html) [@miniCRAN] and [checkpoint](https://cran.r-project.org/web/packages/checkpoint/vignettes/checkpoint.html) [@checkpoint]. Notable is also the package [`reprex`](https://github.com/tidyverse/reprex) [**repr**oducible **ex**ample, @reprex], but its scope is limited to small examples.
